---
title: "Test_Document"
author: "Adolfo Morales"
date: "March 30, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data

```{r LoadingData,echo=TRUE}
rm(list=ls())
setwd("C:/Users/amora/OneDrive/Documents/R_Projects/Coursera/Reproducable_research/Project_1")
activity<-read.csv("activity.csv",header=TRUE,na.strings="NA")
activity$steps<-as.numeric(activity$steps)
```

## What is the mean number of steps taken per day?

Creating Histogram with Steps taken per day
```{r StepsPerDay,echo=TRUE}
TotalSteps<-as.data.frame(with(activity,tapply(steps,date,sum,na.rm=TRUE)))
colnames(TotalSteps)<-c("Steps")
hist(TotalSteps$Steps,main=paste("Histogram of Steps Takes"),xlab="Steps per Day")
```

Calculating Mean and Median of Steps
```{r MeanMedian,echo=TRUE}
StepsSummary<-summary(TotalSteps$Steps)
StepsSummary[3]
StepsSummary[4]
```


## What is the average daly activity pattern?

Making a time series plot
```{r MakingTimePlot,echo=TRUE}
ActivitySummary<-as.data.frame(with(activity,tapply(steps,interval,mean,na.rm=TRUE)))
ActivitySummary$Interval<-rownames(ActivitySummary)
colnames(ActivitySummary)<-c("Avg_Steps","Interval")
plot(x=ActivitySummary$Interval,ActivitySummary$Avg_Steps,
     type="l",
     main="Avg Steps per time Interval",
     xlab="Interval",
     ylab="Avg Steps taken per 5 minutes interval",
     col="blue")
```

Which Interval has the maximun number of steps?
``` {r MaxSteps,echo=TRUE}
max.steps<-which.max(ActivitySummary$Avg_Steps)
ActivitySummary[max.steps,]
```


## Inputing Missing Values

Determining number of NAs in the Steps Column
``` {r NAs,echo=TRUE}
activity.summary<-summary(activity$steps)
activity.summary[7]
```

Replacing NAs with Average for that interval
``` {r ReplacingNAs,echo=TRUE}
activity2<-activity
for (i in 1:length(activity2$steps)) {
        if (is.na(activity2[i,1])==TRUE) {
                activity2[i,1]<-ActivitySummary[which(ActivitySummary$Interval==activity2[i,3]),1]
        }
}
```

## Making Histogram with new data

``` {r Newhistogram,echo=TRUE}
TotalSteps2<-as.data.frame(with(activity2,tapply(steps,date,sum,na.rm=TRUE)))
colnames(TotalSteps2)<-c("Steps")
hist(TotalSteps$Steps,main=paste("Histogram of Steps Takes"),xlab="Steps per Day")
```

Calculating Mean and Median of Steps
```{r MeanMedian2,echo=TRUE}
StepsSummary<-summary(TotalSteps2$Steps)
StepsSummary[3]
StepsSummary[4]
```


Making weekday calculations
``` {r weekdays1,echo=TRUE}
## Making Factor for Weekday / Weekend
activity2$weekday<-as.factor(weekdays(as.Date(activity2$date)))
activity2$wd<-as.factor(ifelse(activity2$weekday %in% c("Saturday","Sunday"), "Weekend","Weekday"))

## Taking Averages
#Weekend
activity2.weekend<-activity2[activity2$wd=="Weekend",]
ActivitySummary2.weekend<-as.data.frame(with(activity2.weekend,tapply(steps,interval,mean,na.rm=TRUE)))
ActivitySummary2.weekend$Interval<-rownames(ActivitySummary2.weekend)
colnames(ActivitySummary2.weekend)<-c("Weekend_Steps","Interval")
ActivitySummary2.weekend$Weekend_Steps<-as.numeric(ActivitySummary2.weekend$Weekend_Steps)

#Weekdays
activity2.weekday<-activity2[activity2$wd=="Weekday",]
ActivitySummary2.weekday<-as.data.frame(with(activity2.weekday,tapply(steps,interval,mean,na.rm=TRUE)))
ActivitySummary2.weekday$Interval<-rownames(ActivitySummary2.weekday)
colnames(ActivitySummary2.weekday)<-c("Weekday_Steps","Interval2")
ActivitySummary2.weekday$Weekday_Steps<-as.numeric(ActivitySummary2.weekday$Weekday_Steps)

#Merging
final.df<-cbind(ActivitySummary2.weekend,ActivitySummary2.weekday)

#Plotting
plot(x=ActivitySummary2.weekend$Interval,y=ActivitySummary2.weekend$Weekend_Steps,
     main="Steps per Time Interval by Weekday / Weekend",
     ylab="Avg. Steps Taken",
     xlab="Time Interval",
     type="l",
     ylim=c(0,250),
     col="blue")
lines(x=ActivitySummary2.weekday$Interval,y=ActivitySummary2.weekday$Weekday_Steps,
      col="red")
legend("topright",legend=c("Weekend","Weekday"),lty=c(1,1),col=c("blue","red"))

```










